cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Updated gen_gridcube

@@

>>>>

The `gen_gridcube(n, p)` constructs a regular grid using approximately $n$ points by evenly partitioning each of the $p$ dimensions. Specifically, the number of grid points along each axis is determined by `gen_nproduct(n, p)`, which calculates the nearest balanced integer factors whose product is close to $n$. The full grid is generated via `expand_grid()`, giving Cartesian combinations of these evenly spaced positions.

Each variable $X\_j$ represents integer grid coordinates (e.g., 1, 2, 3, ...) in dimension $j$:

$$
X\_j \in {1, \dots, k\_j},\text{ where }\prod\_{j=1}^p k\_j \approx n.
$$

This results in a hypercube-shaped lattice in $p$-dimensional space.

@@

- Grided cube: This function is useful for assessing how algorithms preserve uniformly spaced data in high-dimensional spaces.
